Trauma treatment delay

### 2023-11-17 manuscriptlongversion.Rmd
text

Out of the 14,022, 5,710 patients were not screened for ofi, which
excludes them from the study. Out of the remaining 8,312 patients, 1,823
patients had missing data in one or more of the analysed parameters,
which led to exclusion from the study.

In the remaining group of 6,489 patients who have been screened for ofi
and have data registered in all parameters examined for the study, 69
patients were found to have received delayed treatment during their stay
at the hospital.

@@

7,051 patients included in the first logistical regression. 69% of the
individuals included were men, with the remaining 31% being women. The
mean value for the ISS score was 11.30, with the standard deviation
being 13.22. The majority of the patients had General care department as
their highest care level, followed by ER, ICU, OR and lastly specialized
care department. The majority of patients, 82%, were not intubated
during their stay in the hospital, followed by 9.2% intubated at the
hospital and 8.4% intubated prehospitaly. The mean age of the patients
was 44.95 years old, with a standard deviation of 21.37. Most of the
patients arrived during on-call hour, 60%, with the rest arriving during
working hours. 67% of the patients arrived on a weekday, with the rest
arriving on the weekend.

@@

As the table below shows, most of the variables, when adjusted for, does
not have an effect on the risk of receiving delayed treatment. Only two
values in one of the categories had an effect, having ICU or OR compared
to having ER as your highest care level. It suggests that patients who
were in the ICU or OR as their highest care level had a lower chance of
receiving delayed treatment compared with patients who had ER as their
highest.

@@

For the second logistical regression, we had a group size of 7,344
patients, with 70 of them having received delayed treatment. The reason
for this group having more patients is because of the exclusion criteria
that patients can't have data missing in any of the examined variables.
In this group, fewer patients had missing data, leading to fewer
exclusions. This resulted in different values in the same variables as
previously used in the first logistical regression. 68% of the
individuals included were men, with the remaining 32% being women. The
mean value for the ISS score was 10.07, with the standard deviation
being 10.27. The mean age of the patients was 44.20 years old, with a
standard deviation of 21.41. The majority of the patients had no
emergency measures performed, with 76% of the patients belonging to this
group. Following this, the most common emergency procedures were other
action, laparotomy, craniotomy, radiological intervention, intracranial
pressure measurement, and lastly, revascularization. The mean SBP was
137.60, with a standard deviation of 25.09. Mean respiratory rate was
18.59 with a standard deviation of 5.10. Lastly, mean GCS was 13.95,
with a standard deviation of 2.58.

@@

The analysis shows that when adjusted for, most variables do not have a
correlation with receiving delayed treatment.

>>>>

Out of the 14,022 patients receiving trauma care at Karolinska
University Hospital, 5,710 patients were not screened for ofi, which
excludes them from the study and leaves 8,312 patients that have been
screened for ofi.

As were running two logistical regression models with different
variables and a missing value in a variable led to exclusion, the two
groups did not have the same amount of participants. In the first
logistical regression, 1,261 patients had missing data in one or more of
the analysed parameters which left 7,051 individuals group, 69 of which
hade delayed treatment. In the second logistical regression, 1,038
patients had missing data in one or more of the analysed parameters
which left 7,274 individuals group, 70 of which hade delayed treatment.

@@

The 7,051 patients included in the first logistical regression had
characteristics as shown in table1. 69% of the individuals included were
men, with the remaining 31% being women. The mean value for the ISS
score was 11.30, with the standard deviation being 13.22. The majority
of the patients had General care department as their highest care level,
followed by ER, ICU, OR and lastly specialized care department. The
majority of patients, 82%, were not intubated during their stay in the
hospital, followed by 9.2% intubated at the hospital and 8.4% intubated
prehospitaly. The mean age of the patients was 44.95 years old, with a
standard deviation of 21.37. Most of the patients arrived during on-call
hour, 60%, with the rest arriving during working hours. 67% of the
patients arrived on a weekday, with the rest arriving on the weekend.

@@

As the table below shows, most of the variables, when adjusted for, does
not have an effect on the risk of receiving delayed treatment. Only when
not adjusted for, not being intubated had a correlation with increased
incidence of delayed treatment, while having higher ISS had the inverse
effect with lowering the rate of delayed treatment. Only two values in
one of the categories had an effect, having ICU or OR compared to having
ER as your highest care level. It suggests that patients who were in the
ICU or OR as their highest care level had a lower chance of receiving
delayed treatment compared with patients who had ER as their highest.

@@

Below are the characteristics of the group used in the second logistical
regression. In this group, fewer patients had missing data, leading to
fewer exclusions. This resulted in different values in the same
variables as previously used in the first logistical regression. 68% of
the individuals included were men, with the remaining 32% being women.
The mean value for the ISS score was 10.07, with the standard deviation
being 10.27. The mean age of the patients was 44.20 years old, with a
standard deviation of 21.41. The majority of the patients had no
emergency measures performed, with 76% of the patients belonging to this
group. Following this, the most common emergency procedures were other
action, laparotomy, craniotomy, radiological intervention, intracranial
pressure measurement, and lastly, revascularization. The mean SBP was
137.60, with a standard deviation of 25.09. Mean respiratory rate was
18.59 with a standard deviation of 5.10. Lastly, mean GCS was 13.95,
with a standard deviation of 2.58.

@@

The analysis shows that when adjusted for, most variables do not have a
correlation with receiving delayed treatment. Three variables, ISS, RR
and GCS, had a correlation with receiving delayed treatment when not
adjusted for. However, when adjusted for, the correlation dissapeared.
In the case of emergency procedure, there was a correlation for all
emergency procedures performed and having a lowered incidence of delayed
treatment among the patients, compared with not receiving any emergency
measures performed.
